Systematic studies of correlations between different order flow harmonics in $\PbPb$ collisions at $\snn = 2.76$~TeV

### 2016-12-02 longSC.tex
version to sami

The existing measurements provide an estimate only of the average value of QGP's $\eta/s$, both at RHIC and LHC energies. What remains completely unknown is how the $\eta/s$ of QGP depends on temperature ($T$). This study has been just initiated by the theorists in Ref.~\cite{Niemi:2015qia}, where the first (and only rather qualitative) possibilities where investigated (see Fig.~1 therein). The emerging picture is that the study of individual flow harmonics $v_n$ will unlikely reveal the details of $\eta/s(T)$ dependence.
It was demonstrated already in \cite{Niemi:2015qia} that different $\eta/s(T)$ parameterizations can lead to the same centrality dependence of individual flow harmonics. In Ref.~\cite{Niemi:2012aj} new flow observables were introduced which quantify the degree of correlation between two different harmonics $v_m$ and $v_n$. These new observables have potential to discriminate the contributions to anisotropic flow development from initial conditions and from the transport properties of the QGP~\cite{Niemi:2012aj}. Therefore their measurements would provide the experimental constrains of the theoretical predictions for individual stages of heavy-ion evolution independently. In addition, it turned out that correlations of different flow harmonics are sensitive to the temperature dependence of $\eta/s$~\cite{ALICE:2016kpq}, to which individual flow harmonics are weakly sensitive~\cite{Niemi:2015qia}.

@@

%\noindent\textbf{\textcolor{blue}{[Review of recent theoretical papers which discuss SC.]}} 
The SC observables provide independent information to that obtained from recently measured symmetry plane correlators in \cite{ALICE:2011ab,Adare:2011tg,Aad:2014fla}. This statement does not exclude the possibility that both set of observables can be sensitive to the same physical mechanisms. In the recent theoretical study~\cite{Giacalone:2016afq} it was pointed out that the mechanism giving rise to symmetry plane correlations (nonlinear coupling) can also contribute to symmetric cumulants. As an  example, the existing correlation due to hydrodynamic evolution between $V_4$ and $V_2^2$ (which are vectors in the transverse plane) implies that both the angles and the magnitudes are correlated~\cite{Giacalone:2016afq}.

Interpretation of flow results obtained with multiparticle correlation techniques in small colliding systems, like pp and p--Pb at LHC, remains a challenge. The underlying difficulty stems from the fact that when anisotropic flow harmonic $v_n$ is estimated with $k$-particle correlator, the statistical spread of that estimate scales to leading order as $\sigma_{v_{n}}\sim\frac{1}{\sqrt{N}}\frac{1}{M^{k/2}}\frac{1}{v_{n}^{k-1}}$, where $M$ is the number of particles in an event (multiplicity) and $N$ is total number of events. This generic scaling ensures that multiparticle correlations are precision method only in heavy-ion collisions, characterized both with large values of multiplicity and flow. To leading order the measurements in small systems~\cite{Aad:2013fja,Abelev:2014mda,Khachatryan:2015waa,Adamczyk:2015xjc,Adare:2015ctn} and the measurements in heavy-ion collisions resemble the same features, which can be attributed to collective anisotropic flow in both cases. However, such interpretation is challenged by the outcome of recent Monte Carlo study~\cite{Loizides:2016tew} for $e^+e^-$ systems in which collective effects are not expected. Nonetheless, in this study to leading order multiparticle correlations exhibit yet again the similar universal trends first seen in heavy-ion collisions, both for elliptic and triangular flow. Therefore, it seems unlikely that the analysis of individual flow harmonics with multiparticle techniques will answer whether collective effects can develop and QGP be formed in small systems---instead new observables, like SC, might provide the final answer due to their better sensitivity~\cite{Niemi:2012aj,ALICE:2016kpq}.

@@

Another large contribution to the systematic uncertainty originates from the non-uniform reconstruction efficiency. In order to estimate its effects, we use the AMPT model (see Sec.~\ref{sec:theory}) which have flat uniform distribution of azimuthal angles.
Detector inefficiencies was introduced to mimic non-uniform azimuthal distribution in the data. For the observables SC(5,2), SC(5,3) and SC(4,3) variation due to non-uniform acceptance is about 9\%, 17\% and 11\%, respectively.
Overall, the systematic uncertainties are larger for the SC(5,3) and SC(5,2) than for the lower harmonics of SC$(m,n)$.
This is because $v_{n}$ are decreasing with n increasing and become more sensitive to azimuthal modulation due to detector imperfections. 
%Furthermore, the various AMPT models (see the details in Sec.~\ref{sec:theory}) were used to check the sensitivities of the observables due to the strength of the signals we are measuring, it turned out that the effect is negligible.

@@

The VISH2+1~\cite{Shen:2010uy,Shen:2014vra} event-by-event calculations for relativistic heavy-ion collisions are based on (2+1)-dimensional viscous hydrodynamics which describes both the QGP phase and the highly dissipative and even off-equilibrium late hadronic stage with fluid dynamics. With well tuned transport coefficients, decoupling temperature  and given initial condition discussed later, it could describe the $p_{\rm T}$ spectra and different flow harmonics at RHIC and the LHC~\cite{Qiu:2011hf, Shen:2010uy, Shen:2011eg, Bhalerao:2015iya}.
Three different initial conditions ({MC-Glauber}, {MC-KLN} and {AMPT}) along with different constant $\eta/s$ values are used in the model~\cite{Zhu:2016puf}. 
Traditionally, the Glauber model constructs the initial entropy density from contributions of the wounded nucleon and binary collision density profiles~\cite{Kolb:2000sd}, and the {KLN} model assumes that the initial entropy density is proportional to the initial gluon density calculated from the corresponding $k_T$ factorization formula~\cite{Kharzeev:2000ph}. In the Monte Carlo versions ({MC-Glauber} and {MC-KLN})~\cite{Miller:2007ri,Drescher:2006ca,Hirano:2009ah}, additional initial state fluctuations are introduced through the position fluctuation of individual nucleons inside the colliding nuclei. For the {AMPT} initial conditions~\cite{Bhalerao:2015iya,Pang:2012he,Xu:2016hmp}, the fluctuating energy density profiles are constructed from the energy decompositions of individual partons, which fluctuate in both momentum and position coordinate. Compared with the {MC-Glauber} and {MC-KLN} initial conditions, the additional Gaussian smearing parameter in the {AMPT} initial conditions makes the typical initial fluctuation scales changeable which gives rise to non-vanishing initial local flow velocities~\cite{Pang:2012he}.
%The AMPT initial conditions is basically HIJING with the location of the strings specified according to the sites of the nucleon nucleon collisions. The model then introduces the string melting procedure to produce initial partons. These partons are then evolved for the short duration using the ZPC parton cascade model. Instead the initial energy momentum tensor is directly fed into the hydrodynamic calculations, the energy density and the flow velocity are first obtained using the Landau condition and only the ideal fluid parts are used as the initial condition for the hydrodynamic evolution. Mini-jets from semi-hard parton scatterings are assumed to be locally thermalized through a Gaussian smearing and give rise to non-vanishing initial local flow velocities~\cite{Pang:2012he}.

@@

%The centrality dependence of SC(4,2) and SC(3,2) are presented in Fig.~\ref{fig:Figure_1} as shadow bands which are the same as the published results~\cite{ALICE:2016kpq}. Positive values of SC(4,2) are observed for all measured centralities. This suggests a positive correlation between the event-by-event fluctuations of $v_2$ and $v_4$. It also indicates that finding $v_2$ larger than average ($\langle v_2 \rangle$) in an event enhances the probability of finding $v_4$ larger than average ($\langle v_4 \rangle$) in that event. On the other hand, the negative results of SC(3,2) over all measured centralities show the anti-correlation between $v_2$ and $v_3$ flow harmonic magnitudes, which further implies that finding $v_2$ larger than average ($v_2 > \langle v_2 \rangle$) enhancing the probability of finding smaller $v_3$ than average ($v_3 < \langle v_3 \rangle$).

% \begin{figure}[htbp]
%            \begin{center}
%                       \resizebox{0.48\textwidth}{!}{\includegraphics{figs/fig1_QConly.eps}}
%                       \resizebox{0.48\textwidth}{!}{\includegraphics{figs/fig1_QConly_norm.eps}}
%             \caption{The results of SC(3,2)(blue markers) and SC(4,2)(red markers)  with 0.2 $<p_{\rm T}<$ 5.0 GeV/c and $ | \eta | < 0.8$ GeV/$c$ as function of collision centrality (Left). The normalized SC$(m,n)$ (NSC) results which are scaled with $\langle v_m^2 \rangle \langle v_n^2 \rangle $ are shown on the right.}
%              \label{fig:Figure_1}
%              \end{center}
% \end{figure}

%\begin{figure}[h]
%	\begin{center}
%       	\resizebox{0.48\columnwidth}{!}{\includegraphics{figs/SC_Comparison_SC32_HIJING_ptdep.eps}}
%        	\resizebox{0.48\columnwidth}{!}{\includegraphics{figs/SC_Comparison_SC42_HIJING_ptdep.eps}}
%        \caption{Result of SC(3,2) and SC(4,2) with HIJING simulations. Defaults($0.2 < p_{\rm T} < 5.0GeV/c$) are drawn as full square with blue color, and different minimum cut conditions are listed in legend. A small shifts along the x axis were applied for better visibility.}
%        \label{fig:results_HIJING}
%        \end{center}   
%\end{figure}

@@

However, unlike SC$(m,n)$, the NSC$(m,n)$ results with the higher order flow harmonics show almost same order of the correlation strength as the lower order flow harmonic correlations (NSC(3,2) or NSC(4,2)).
NSC(4,3) magnitude is comparable to NSC(3,2) and one finds that a hierarchy, NSC(5,3) $>$ NSC(4,2) $>$ NSC(5,2), holds for centrality ranges $>20\%$ within the errors shown on the right in Fig.~\ref{fig:Figure_1}.
These results indicate that the lower order harmonic correlations (SC(3,2) and SC(4,2)) are larger than higher order harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)), not only because of the correlation strength itself but also because of the strength of individual flow harmonics. 
SC(5,2) is stronger than SC(5,3), but as for NSC, the normalized correlation between $v_5$ and $v_3$ is stronger than the normalized correlation between $v_5$ and $v_2$.

It can be seen in Fig.~\ref{fig:Figure_1} that the lower order harmonic correlations (SC(3,2) and SC(4,2)) and SC(5,2) increase non-linearly toward peripheral collisions.
In case of SC(5,3) and SC(4,3), the centrality dependence is weaker than the other harmonic correlations and a monotonic increase is observed for these harmonic correlations.
NSC(5,3) shows the strongest correlation among all harmonics and NSC(4,2), NSC(5,2) shows a weak centrality dependence.
Both NSC(3,2) and NSC(4,3) show a monotonic increase toward peripheral collisions with the similar magnitude.

To study the $p_{\rm T}$ dependence of SC$(m,n)$, we change the low $p_{\rm T}$ cut-off, instead of using independent $p_{\rm T}$ interval, in order to avoid large statistical fluctuations in the results. Various minimum $p_{\rm T}$ cuts from 0.2 to 1.5~GeV/$c$ are applied.
The results of $p_{\rm T}$ dependence of SC(3,2) and SC(4,2) with minimum $p_{\rm T}$ cuts, $0.2<p_{\rm T}<0.7$~GeV/$c$, are shown on the left top in Fig.~\ref{fig:Figure_2}.
The strength of SC$(m,n)$ becomes larger as the minimum $p_{\rm T}$ increases. 
%This indicates that the relationship between event-by-event fluctuations of two different flow harmonics $v_m$ and $v_n$ is stronger for high $p_{\rm T}$ particles. 
This $p_{\rm T}$ dependent correlations have much stronger centrality dependence, where SC$(m,n)$ gets much larger as the centrality or the minimum $p_{\rm T}$ cut increase. 
NSC(3,2) and NSC(4,2) with different minimum cuts are shown on the right in Fig.~\ref{fig:Figure_2}.
The strong $p_{\rm T}$ dependence observed in SC$(m,n)$ is not seen in NSC$(m,n)$. The NSC$(m,n)$ results are aligned all together and consistent in errors for all minimum $p_{\rm T}$ cuts. 
This indicates that the $p_{\rm T}$ dependence of SC$(m,n)$ is dominated by the $p_{\rm T}$  dependence of $\left<v_n\right>$ values. 
The minimum $p_{\rm T}$ cuts are extended from 0.8  to 1.5~GeV/$c$ and the results are shown on the bottom panels in Fig.~\ref{fig:Figure_2}.
While SC$(m,n)$ show the similar trends as for $p_{\rm T}<0.8$~GeV/$c$, NSC$(m,n)$ tends to decrease with increasing $p_{\rm T}$ or the centrality.
The $p_{\rm T}$ dependence for NSC(3,2) is not clearly seen and it is consistent with no $p_{\rm T}$ dependence within the current statistical and systematic errors for the centrality range $<$30\% and shows moderate decreasing trend for increasing $p_{\rm T}$ for $>$30\% centrality range.
NSC(4,2) shows a moderate decreasing trend as $p_{\rm T}$ or the centrality increase. These observations are strikingly different from $p_{\rm T}$ dependence of individual flow harmonics, where the relative flow fluctuations $\sigma_{v_2}/\langle v_{2} \rangle$~\cite{Voloshin:2008dg} are independent of momentum up to $p_{\rm T}$ $\sim$ 8~GeV/$c$ (see Fig. 3 in Ref.~\cite{Abelev:2012di}).
%(see further discussions in Sec.~\ref{sec:ptdepsc})
%This might be an indication of possible viscous corrections for the equilibrium distribution at hadronic freeze-out~\cite{Luzum:2010ad}.
%However within the current statistical and systematic errors, it is consistent with no $p_{\rm T}$ dependence of NSC$(m,n)$ (see further discussions in Sec.~\ref{sec:ptdepsc}).

\begin{figure*}
	\begin{center}
        	\resizebox{0.48\columnwidth}{!}{\includegraphics{figs/fig4_QConly_SC_ptdep}}
        	\resizebox{0.48\columnwidth}{!}{\includegraphics{figs/fig4_QConly_nSC_ptdep}}
	\resizebox{0.48\columnwidth}{!}{\includegraphics{figs/fig4b_QConly_SC_ptdep}}
        	\resizebox{0.48\columnwidth}{!}{\includegraphics{figs/fig4b_QConly_nSC_ptdep}}
        \caption{SC(3,2) and SC(4,2) with various minimum $p_{\rm T}$ cuts ((a) and (c)) and results of normalized SC(3,2) and SC(4,2) ((b) and (d)). The panel (a) and (b) show the results for minimum $p_{\rm T}$ range, $0.2<p_{\rm T}<0.7$~GeV/$c$ and the panel (c) and (d) are for minimum $p_{\rm T}$ range, $0.8<p_{\rm T}<1.5$~GeV/$c$. Note that NSC data points from each minimum $p_{\rm T}$ in a centrality percentile bin are shifted for visibility.}
        \label{fig:Figure_2}
        \end{center}   
\end{figure*}

@@

>>>>

The existing measurements provide an estimate of the average value of QGP's $\eta/s$, both at RHIC and LHC energies. What remains uncertain is how the $\eta/s$ of QGP depends on temperature ($T$)~\cite{Niemi:2015qia}. This study has been just initiated by the theorists in Ref.~\cite{Niemi:2015qia}, where the first (and only rather qualitative) possibilities where investigated (see Fig.~1 therein). The emerging picture is that the study of individual flow harmonics $v_n$ will unlikely reveal the details of $\eta/s(T)$ dependence.
It was demonstrated already in \cite{Niemi:2015qia} that different $\eta/s(T)$ parameterizations can lead to the same centrality dependence of individual flow harmonics. In Ref.~\cite{Niemi:2012aj} new flow observables were introduced which quantify the degree of correlation between two different harmonics $v_m$ and $v_n$. These new observables have potential to discriminate the contributions to anisotropic flow development from initial conditions and from the transport properties of the QGP~\cite{Niemi:2012aj}. Therefore their measurements would provide the experimental constrains of the theoretical predictions for individual stages of heavy-ion evolution independently. In addition, it turned out that correlations of different flow harmonics are sensitive to the temperature dependence of $\eta/s$~\cite{ALICE:2016kpq}, to which individual flow harmonics are weakly sensitive~\cite{Niemi:2015qia}.

@@

@@

Another large contribution to the systematic uncertainty originates from the non-uniform reconstruction efficiency in azimuthal angle. In order to estimate its effects, we use the AMPT model (see Sec.~\ref{sec:theory}) which have flat uniform distribution of azimuthal angles.
Detector inefficiencies was introduced to mimic non-uniform azimuthal distribution in the data. For the observables SC(5,2), SC(5,3) and SC(4,3) variation due to non-uniform acceptance is about 9\%, 17\% and 11\%, respectively.
Overall, the systematic uncertainties are larger for the SC(5,3) and SC(5,2) than for the lower harmonics of SC$(m,n)$.
This is because $v_{n}$ are decreasing with n increasing and become more sensitive to azimuthal modulation due to detector imperfections. 
%Furthermore, the various AMPT models (see the details in Sec.~\ref{sec:theory}) were used to check the sensitivities of the observables due to the strength of the signals we are measuring, it turned out that the effect is negligible.

@@

The VISH2+1~\cite{Shen:2010uy,Shen:2014vra} event-by-event calculations for relativistic heavy-ion collisions are based on (2+1)-dimensional viscous hydrodynamics which describes both the QGP phase and the highly dissipative and even off-equilibrium late hadronic stage with fluid dynamics. With well tuned transport coefficients, decoupling temperature  and given initial condition discussed later, it could describe the $p_{\rm T}$ spectra and different flow harmonics at RHIC and the LHC~\cite{Qiu:2011hf, Shen:2010uy, Shen:2011eg, Bhalerao:2015iya}.
Three different initial conditions ({MC-Glauber}, {MC-KLN} and {AMPT}) along with different constant $\eta/s$ values are used in the model~\cite{Zhu:2016puf}. 
Traditionally, the Glauber model constructs the initial entropy density from contributions of the wounded nucleon and binary collision density profiles~\cite{Kolb:2000sd}, and the {KLN} model assumes that the initial entropy density is proportional to the initial gluon density calculated from the corresponding $k_T$ factorization formula~\cite{Kharzeev:2000ph}. In the Monte Carlo versions ({MC-Glauber} and {MC-KLN})~\cite{Miller:2007ri,Drescher:2006ca,Hirano:2009ah}, additional initial state fluctuations are introduced through the position fluctuation of individual nucleons inside the colliding nuclei. For the {AMPT} initial conditions~\cite{Bhalerao:2015iya,Pang:2012he,Xu:2016hmp}, the fluctuating energy density profiles are constructed from the energy decompositions of individual partons, which fluctuate in both momentum and position coordinate. Compared with the {MC-Glauber} and {MC-KLN} initial conditions, the additional Gaussian smearing in the {AMPT} initial conditions gives rise to non-vanishing initial local flow velocities~\cite{Pang:2012he}.
%The AMPT initial conditions is basically HIJING with the location of the strings specified according to the sites of the nucleon nucleon collisions. The model then introduces the string melting procedure to produce initial partons. These partons are then evolved for the short duration using the ZPC parton cascade model. Instead the initial energy momentum tensor is directly fed into the hydrodynamic calculations, the energy density and the flow velocity are first obtained using the Landau condition and only the ideal fluid parts are used as the initial condition for the hydrodynamic evolution. Mini-jets from semi-hard parton scatterings are assumed to be locally thermalized through a Gaussian smearing and give rise to non-vanishing initial local flow velocities~\cite{Pang:2012he}.

@@

@@

However, unlike SC$(m,n)$, the NSC$(m,n)$ results with the higher order flow harmonics show almost same order of the correlation strength as the lower order flow harmonic correlations (NSC(3,2) or NSC(4,2)).
NSC(4,3) magnitude is comparable to NSC(3,2) and one finds that a hierarchy, NSC(5,3) $>$ NSC(4,2) $>$ NSC(5,2), holds for centrality ranges $>20\%$ within the errors shown on the panel (b) in Fig.~\ref{fig:Figure_1}.
These results indicate that the lower order harmonic correlations (SC(3,2) and SC(4,2)) are larger than higher order harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)), not only because of the correlation strength itself but also because of the strength of individual flow harmonics. 
SC(5,2) is stronger than SC(5,3), but as for NSC, the normalized correlation between $v_5$ and $v_3$ is stronger than the normalized correlation between $v_5$ and $v_2$.

It can be seen on the panel (a) in Fig.~\ref{fig:Figure_1} that the lower order harmonic correlations (SC(3,2) and SC(4,2)) and SC(5,2) increase non-linearly toward peripheral collisions.
In case of SC(5,3) and SC(4,3), the centrality dependence is weaker than the other harmonic correlations and a monotonic increase is observed for these harmonic correlations.
NSC(5,3) shows the strongest correlation among all harmonics and NSC(4,2), NSC(5,2) shows a weak centrality dependence.
Both NSC(3,2) and NSC(4,3) show a monotonic increase toward peripheral collisions with the similar magnitude.

To study the $p_{\rm T}$ dependence of SC$(m,n)$, we change the low $p_{\rm T}$ cut-off, instead of using independent $p_{\rm T}$ interval, in order to avoid large statistical fluctuations in the results. Various minimum $p_{\rm T}$ cuts from 0.2 to 1.5~GeV/$c$ are applied.
The results of $p_{\rm T}$ dependence of SC(3,2) and SC(4,2) with minimum $p_{\rm T}$ cuts, $0.2<p_{\rm T}<0.7$~GeV/$c$, are shown on the panel (a) in Fig.~\ref{fig:Figure_2}.
The strength of SC$(m,n)$ becomes larger as the minimum $p_{\rm T}$ increases. 
%This indicates that the relationship between event-by-event fluctuations of two different flow harmonics $v_m$ and $v_n$ is stronger for high $p_{\rm T}$ particles. 
This $p_{\rm T}$ dependent correlations have much stronger centrality dependence, where SC$(m,n)$ gets much larger as the centrality or the minimum $p_{\rm T}$ cut increase. 
NSC(3,2) and NSC(4,2) with different minimum cuts are shown on the panel (b) and (d) in Fig.~\ref{fig:Figure_2}.
The strong $p_{\rm T}$ dependence observed in SC$(m,n)$ is not seen in NSC$(m,n)$. The NSC$(m,n)$ results are aligned all together and consistent in errors for all minimum $p_{\rm T}$ cuts. 
This indicates that the $p_{\rm T}$ dependence of SC$(m,n)$ is dominated by the $p_{\rm T}$  dependence of $\left<v_n\right>$ values. 
The minimum $p_{\rm T}$ cuts are extended from 0.8  to 1.5~GeV/$c$ and the results are shown on the panel (c) and (d) in Fig.~\ref{fig:Figure_2}.
While SC$(m,n)$ show the similar trends as for $p_{\rm T}<0.8$~GeV/$c$, NSC$(m,n)$ tends to decrease with increasing $p_{\rm T}$ or the centrality.
The $p_{\rm T}$ dependence for NSC(3,2) is not clearly seen and it is consistent with no $p_{\rm T}$ dependence within the current statistical and systematic errors for the centrality range $<$30\% and shows moderate decreasing trend for increasing $p_{\rm T}$ for $>$30\% centrality range.
NSC(4,2) shows a moderate decreasing trend as $p_{\rm T}$ or the centrality increase. These observations are strikingly different from $p_{\rm T}$ dependence of individual flow harmonics, where the relative flow fluctuations $\sigma_{v_2}/\langle v_{2} \rangle$~\cite{Voloshin:2008dg} are independent of momentum up to $p_{\rm T}$ $\sim$ 8~GeV/$c$ (see Fig. 3 in Ref.~\cite{Abelev:2012di}).
%(see further discussions in Sec.~\ref{sec:ptdepsc})
%This might be an indication of possible viscous corrections for the equilibrium distribution at hadronic freeze-out~\cite{Luzum:2010ad}.
%However within the current statistical and systematic errors, it is consistent with no $p_{\rm T}$ dependence of NSC$(m,n)$ (see further discussions in Sec.~\ref{sec:ptdepsc}).

\begin{figure*}
	\begin{center}
        	\resizebox{0.44\columnwidth}{!}{\includegraphics{figs/fig4_QConly_SC_ptdep}}
        	\resizebox{0.44\columnwidth}{!}{\includegraphics{figs/fig4_QConly_nSC_ptdep}}
	\resizebox{0.44\columnwidth}{!}{\includegraphics{figs/fig4b_QConly_SC_ptdep}}
        	\resizebox{0.44\columnwidth}{!}{\includegraphics{figs/fig4b_QConly_nSC_ptdep}}
        \caption{SC(3,2) and SC(4,2) with various minimum $p_{\rm T}$ cuts ((a) and (c)) and results of normalized SC(3,2) and SC(4,2) ((b) and (d)). The panel (a) and (b) show the results for minimum $p_{\rm T}$ range, $0.2<p_{\rm T}<0.7$~GeV/$c$ and the panel (c) and (d) are for minimum $p_{\rm T}$ range, $0.8<p_{\rm T}<1.5$~GeV/$c$. Note that NSC data points from each minimum $p_{\rm T}$ in a centrality percentile bin are shifted for visibility.}
        \label{fig:Figure_2}
        \end{center}   
\end{figure*}

@@

\section{Discussion}
Interpretation of flow results obtained with multiparticle correlation techniques in small colliding systems, like pp and p--Pb at LHC, remains a challenge. The underlying difficulty stems from the fact that when anisotropic flow harmonic $v_n$ is estimated with $k$-particle correlator, the statistical spread of that estimate scales to leading order as $\sigma_{v_{n}}\sim\frac{1}{\sqrt{N}}\frac{1}{M^{k/2}}\frac{1}{v_{n}^{k-1}}$, where $M$ is the number of particles in an event (multiplicity) and $N$ is total number of events. This generic scaling ensures that multiparticle correlations are precision method only in heavy-ion collisions, characterized both with large values of multiplicity and flow. To leading order the measurements in small systems~\cite{Aad:2013fja,Abelev:2014mda,Khachatryan:2015waa,Adamczyk:2015xjc,Adare:2015ctn} and the measurements in heavy-ion collisions resemble the same features, which can be attributed to collective anisotropic flow in both cases. However, such interpretation is challenged by the outcome of recent Monte Carlo study~\cite{Loizides:2016tew} for $e^+e^-$ systems in which collective effects are not expected. Nonetheless, in this study to leading order multiparticle correlations exhibit yet again the similar universal trends first seen in heavy-ion collisions, both for elliptic and triangular flow. Therefore, it seems unlikely that the analysis of individual flow harmonics with multiparticle techniques will answer whether collective effects can develop and QGP be formed in small systems.
Instead observables like SC may shed light on multiparticle correlation measurements in pp and p--Pb. 
%%%instead new observables, like SC, might provide the final answer due to their better sensitivity~\cite{Niemi:2012aj,ALICE:2016kpq}.
